Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-25 main.Rmd
acknowledgement margin fixed
bold label for last figure and for figure 4 no brackets for labels in text

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "figure/",
  fig.align = "center",
  fig.show = "hold",
  cache = TRUE,
  cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
```

@@

\autoref{fig:allFig} (a) shows the distribution of half-hourly electricity consumption through letter value plots across months of the year faceted by quarters of the year. This plot does not work because quarter-of-the-year clashes with month-of-the-year, leading to empty subsets. For example, the first quarter never corresponds to December.

@@

For example, \autoref{fig:allFig} (b) shows the letter value plot across weekday/weekend faceted by quarters of the year and \autoref{fig:allFig} (c) shows the same two cyclic granularities with their mapping reversed. \autoref{fig:allFig} (b) helps us to compare weekday and weekend within each quarter and \autoref{fig:allFig} (c) helps to compare quarters within weekend and weekday.

@@

The Australian authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research. Thanks to [Data61 CSIRO](https://data61.csiro.au/) for partially funding Sayani's research and Dr Peter Toscas for providing useful inputs on improving the analysis of the smart meter application. The package `gravitas` was built during the [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript. More details about the package can be found at [sayani07.github.io/gravitas](https://sayani07.github.io/gravitas/). This article was created with `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown]. The Github repository,  [github.com/Sayani07/paper-gravitas](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "figure/",
  fig.align = "center",
  fig.show = "hold",
  cache = FALSE,
  cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
```

@@

\autoref{fig:allFig}a shows the distribution of half-hourly electricity consumption through letter value plots across months of the year faceted by quarters of the year. This plot does not work because quarter-of-the-year clashes with month-of-the-year, leading to empty subsets. For example, the first quarter never corresponds to December.

@@

For example, \autoref{fig:allFig}b shows the letter value plot across weekday/weekend faceted by quarters of the year and \autoref{fig:allFig}c shows the same two cyclic granularities with their mapping reversed. \autoref{fig:allFig}b helps us to compare weekday and weekend within each quarter and \autoref{fig:allFig}c helps to compare quarters within weekend and weekday.

@@

The Australian authors thank the ARC Centre of Excellence for Mathematical and Statistical Frontiers [(ACEMS)](https://acems.org.au/home) for supporting this research. Thanks to [Data61 CSIRO](https://data61.csiro.au/) for partially funding Sayani's research and Dr Peter Toscas for providing useful inputs on improving the analysis of the smart meter application. We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript. The package `gravitas` was built during the [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). More details about the package can be found at [sayani07.github.io/gravitas](https://sayani07.github.io/gravitas/). The Github repository,  [github.com/Sayani07/paper-gravitas](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials. This article was created with `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown].
